PANCHANGE_data_preprocessing

### 2020-08-20 PANCHANGE_data_preprocessing2020-07-15.Rmd

#Total score comparison between PHQ, PCL and GAD, prepandemic, retrospecive and baseline
PHQ difference scores
```{r phq difference scores}
if(GLAD == TRUE | EDGI == TRUE){
# Difference score for prepandemic and retrospective phq sum scores
dat <- dat %>%
  mutate(
    phq.diff_score_prepan_retro =
      as.numeric(
        phq.sum_score_prepan - phq.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
      )
  )

@@

GAD difference scores
```{r gad difference scores}
if(GLAD == TRUE | EDGI == TRUE){
# Difference score for prepandemic and retrospective gad sum scores
dat <- dat %>%
  mutate(
    gad.diff_score_prepan_retro =
      as.numeric(
        gad.sum_score_prepan - gad.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
      )
  )

@@

OCI-R difference scores
```{r ocir difference scores}
if(GLAD == TRUE | EDGI == TRUE){
# Difference score for prepandemic and retrospective oci-r sum scores
dat <- dat %>%
  mutate(
    ocir.diff_score_prepan_retro =
      as.numeric(
        ocir.sum_score_prepan - ocir.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
      )
  )

>>>>

#Total score comparison between PHQ, PCL and GAD, prepandemic, retrospecive and baseline
PHQ difference scores
```{r phq difference scores}
if(GLAD == TRUE | EDGI == TRUE){
# Difference score for prepandemic and retrospective phq sum scores
dat <- dat %>%
  mutate(
    phq.diff_score_retro_prepan =
      as.numeric(
        phq.sum_score_retro - phq.sum_score_prepan  # retrospective sum score MINUS prepandemic sum score 
      )
  )

@@

GAD difference scores
```{r gad difference scores}
if(GLAD == TRUE | EDGI == TRUE){
# Difference score for prepandemic and retrospective gad sum scores
dat <- dat %>%
  mutate(
    gad.diff_score_retro_prepan =
      as.numeric(
        gad.sum_score_retro - gad.sum_score_prepan  # retrospective sum score MINUS prepandemic sum score 
      )
  )

@@

OCI-R difference scores
```{r ocir difference scores}
if(GLAD == TRUE | EDGI == TRUE){
# Difference score for prepandemic and retrospective oci-r sum scores
dat <- dat %>%
  mutate(
    ocir.diff_score_retro_prepan =
      as.numeric(
        ocir.sum_score_retro - ocir.sum_score_prepan  # retrospective sum score MINUS prepandemic sum score 
      )
  )
